Describing vocalizations in young children: A big data approach through citizen science annotation

### 2021-02-19 202010_jslhr/paper.Rmd
fixed figs in doc

author: 
  - name          : "Chiara Semenzin"
    affiliation   : "1"
    corresponding : no
  - name          : "Lisa Hamrick"
    affiliation   : "2"
    corresponding : no
  - name          : "Amanda Seidl"
    affiliation   : "2"
    corresponding : no
  - name          : "Bridgette Kelleher"
    affiliation   : "2"
    corresponding : no
  - name          : "Alejandrina Cristia"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "29 rue d'Ulm, 75005, Paris, France"
    email         : "alecristia@gmail.com"

@@

author_note: >
       AC acknowledges Agence Nationale de la Recherche (ANR-17-CE28-0007 LangAge, ANR-16-DATA-0004 ACLEW, ANR-14-CE30-0003 MechELex, ANR-17-EURE-0017); and the J. S. McDonnell Foundation (Understanding Human Cognition Scholar Award). LH acknowledges the National Institute of Deafness and Other Communication Disorders (F31DC018219). BK acknowledges the National Institute of Mental Health (K23MH111955) and the Kinley Trust. This publication uses data generated via the Zooniverse.org platform, development of which is funded by generous support, including a Global Impact Award from Google, and by a grant from the Alfred P. Sloan Foundation. The funders had no impact on this study.  All authors approved the final manuscript as submitted, agree to be accountable for all aspects of the work and have no conflict of interests to disclose.

>>>>

author: 
  - name          : "Chiara Semenzin"
    affiliation   : "1"
    corresponding : no
  - name          : "Lisa Hamrick"
    affiliation   : "2"
    corresponding : no
  - name          : "Amanda Seidl"
    affiliation   : "2"
    corresponding : no
  - name          : "Bridgette L. Kelleher"
    affiliation   : "2"
    corresponding : no
  - name          : "Alejandrina Cristia"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "29 rue d'Ulm, 75005, Paris, France"
    email         : "alecristia@gmail.com"

@@

author_note: >
       AC acknowledges Agence Nationale de la Recherche (ANR-17-CE28-0007 LangAge, ANR-16-DATA-0004 ACLEW, ANR-14-CE30-0003 MechELex, ANR-17-EURE-0017), and the J. S. McDonnell Foundation (Understanding Human Cognition Scholar Award); LH  the National Institute of Deafness and Other Communication Disorders (F31DC018219); BK the National Institute of Mental Health (K23MH111955) and the Kinley Trust. This publication uses data generated via the Zooniverse.org platform, development of which is funded by generous support, including a Global Impact Award from Google, and by a grant from the Alfred P. Sloan Foundation. The funders had no impact on this study.  All authors approved the final manuscript as submitted, agree to be accountable for all aspects of the work and have no conflict of interests to disclose.
